### 2024-10-30 PaperSections.Rmd
October 30, before committee meeting

```{r include=FALSE}
library(tidyverse)
library(ggpubr)
library(cowplot)
```

@@

@@

## Survey year proper
p1 <- ggplot(data = acc_surv) +
  geom_line(aes(x = Year, y = acsurv_bm), colour = "#BB2D05", linewidth = 1) +
  geom_point(aes(x = Year, y = acsurv_bm), size = 1.5, shape = 22, colour = "#BB2D05", fill = "#BB2D05") +
  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1995, 2020.9), breaks = c(seq(1995, 2020, 5))) + 
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.009,0), limits = c(0, 1100)) +
  ggtitle("Campelen\na) Spring") +
  theme_classic() +
  theme(legend.position = "none",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.line.x = element_line(size = 0.7), axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))
```

## Survey year proper
p2 <- ggplot(data = acc_surv) +
  geom_line(aes(x = Year, y = acsurv_bm), colour = "#BB2D05", linewidth = 1) +
  geom_point(aes(x = Year, y = acsurv_bm), size = 1.5, shape = 22, colour = "#BB2D05", fill = "#BB2D05") +
  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1981,1995.1), breaks = c(seq(1981,1995, 3))) + 
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.009,0), limits = c(0,6000)) +
  ggtitle("Engel\nb) Spring") +
  theme_classic() +
  theme(legend.position = "none",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.line.x = element_line(size = 0.7), axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))
```

@@

p3 <- ggplot() +
  geom_line(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
  geom_point(aes(x = 0, y = 0, colour = "all"), size = 1.5) +

@@

  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1995,2021), breaks = c(seq(1995, 2021, 5))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.6,2.4)) +
  scale_color_manual(name = "Species Model", values = c(all = "black", surv = "#BB2D05", ap = "#FF7733", gh = "#048BA8"),
                     labels = c(all = "All species", surv = "Acoustic survey", ap = "Plaice", gh = "Greenland halibut")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  ggtitle("c) Spring") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.position = "none",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
        plot.title = element_text(size = 16, face = "bold"))
```

@@

p4 <- ggplot() +
  geom_ribbon(data = ts_df, aes(x = acc_year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
  geom_point(data = ts_df, aes(x = acc_year, y = ts, colour = "all")) +
  geom_line(data = ts_df, aes(x = acc_year, y = ts, colour = "all" ), size = 1.5) +

  scale_x_continuous(name = "Year+1", expand = c(0,0.1), limits = c(1995,2022), breaks = c(seq(1995, 2022, 5))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.45, 1.08)) +
  scale_color_manual(name = "Species Model", values = c(all = "black", ac = "#BC8DA0", gh = "#048BA8"),
                     labels = c(all = "All species", ac = "Cod/ Plaice", gh = "Greenland halibut")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  ggtitle("e) Fall") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.position = "none",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
        plot.title = element_text(size = 16, face = "bold"))
```

  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1981,1995), breaks = c(seq(1981, 1995, 3))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.3,2.0)) +
  scale_color_manual(name = "Species Model", values = c(all = "black", surv = "#BB2D05", ac = "#BC8DA0", gh = "#048BA8"),
                     labels = c(all = "All species", surv = "Acoustic survey", ac = "Cod/ Plaice", gh = "Greenland halibut")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  ggtitle("c) Spring") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.position = "none",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
        plot.title = element_text(size = 16, face = "bold"))
```

p6 <- ggplot() +
  geom_line(aes(x = 0, y = 0, colour = "all"), size = 1.5) +
  geom_point(aes(x = 0, y = 0, colour = "all"), size = 1.5) +

  geom_line(aes(x = 0, y = 0, colour = "ap"), size = 1.5) +
  geom_point(aes(x = 0, y = 0, colour = "ap"), size = 1.5) +

  scale_x_continuous(name = "Year+1", expand = c(0,0.1), limits = c(1981,1995), breaks = c(seq(1981, 1995, 3))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.21,0.75)) +
  scale_color_manual(name = "Species Model", values = c(all = "black", ac = "#BC8DA0", gh = "#048BA8", ap = "#FF7733"),
                     labels = c(all = "All species", ac = "Cod/ Plaice", gh = "Greenland halibut", ap = "American plaice")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  ggtitle("f) Fall") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.position = "none",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
        plot.title = element_text(size = 16, face = "bold"))
```

@@

p7 <- ggarrange(p1+theme(axis.title.x = element_blank()),
          p2+theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
          p3+theme(),
          p5+theme(axis.title.y = element_blank()),
          p4,
          p6+theme(axis.title.y = element_blank()),
          nrow = 3, ncol = 2,
          align = "v", legend = "right", legend.grob = ggpubr::get_legend(p6+theme(legend.position = "right")))

@@

# Linear relationship 
fit <- lm(acc_bm~NLFPM_bm, data = lr_dat)
cor.test(x = lr_dat$NLFPM_bm, y = lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated

lr_dat <- na.omit(lr_dat)

@@

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1995,2020), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
  ggtitle("Campelen\na) Fall 2J3KL All Speices") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = "none",
    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

@@

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1995,2020), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
  ggtitle(" \nb) Spring 3L Plaice") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

@@

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1995,2020), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
  theme_classic() +
  ggtitle(" \nc) Spring 3L Halibut") +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
        legend.position = 'none',
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
        axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

@@

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1981,1995), midpoint = 1987,  low = "blue", mid = "#FFAEFF", high = "red") +
  ggtitle("Engel\nd) Fall 2J3KL Cod/Plaice") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

@@

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1981,1995), midpoint = 1987,  low = "blue", mid = "#FFAEFF", high = "red") +
  theme_classic() +
  ggtitle(" \ne) Fall 2J3KL Halibut") +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

@@

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1984,1995), midpoint = 1990,  low = "blue", mid = "#FFAEFF", high = "red") +
  ggtitle("\nf) Spring 2J3KL Cod/Plaice") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

@@

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1984,1995), midpoint = 1990,  low = "blue", mid = "#FFAEFF", high = "red") +
  theme_classic() +
  ggtitle(" \ng) Spring 2J3KL Halibut") +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))
```

@@

p17 <- ggarrange(p15,p16,
          nrow = 2, ncol = 1, align = "h")

@@

car::influencePlot.lm(fit)

>>>>

```{r include=FALSE}
library(tidyverse)
library(cowplot)
library(ggpubr)
```

@@

## Survey year proper
p1 <- ggplot(data = acc_surv) +
  geom_line(aes(x = Year, y = acsurv_bm), colour = "#BB2D05", linewidth = 1) +
  geom_point(aes(x = Year, y = acsurv_bm), size = 1.5, shape = 22, colour = "#BB2D05", fill = "#BB2D05") +
  scale_x_continuous(name = "Year", expand = c(0.009,0), limits = c(1981,1995.1), breaks = c(seq(1981,1995, 3))) + 
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.009,0), limits = c(0,6000)) +
  ggtitle("Engel\na) Spring") +
  theme_classic() +
  theme(legend.position = "none",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.line.x = element_line(size = 0.7), axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))
```

@@

## Survey year proper
p2 <- ggplot(data = acc_surv) +
  geom_line(aes(x = Year, y = acsurv_bm), colour = "#BB2D05", linewidth = 1) +
  geom_point(aes(x = Year, y = acsurv_bm), size = 1.5, shape = 22, colour = "#BB2D05", fill = "#BB2D05") +
  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1995, 2020.9), breaks = c(seq(1995, 2020, 5))) + 
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)", expand = c(0.009,0), limits = c(0, 1100)) +
  ggtitle("Campelen\nb) Spring") +
  theme_classic() +
  theme(legend.position = "none",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.line.x = element_line(size = 0.7), axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"), 
        plot.title = element_text(size = 16, face = "bold"))
```

p3 <- ggplot() +

  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1981,1995), breaks = c(seq(1981, 1995, 3))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.3,2.0)) +
  scale_color_manual(name = "Species Model", values = c(ac = "#BC8DA0", gh = "#048BA8"),
                     labels = c(ac = "Cod/ Plaice", gh = "Greenland halibut")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  ggtitle("c) Spring") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.position = "none",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
        plot.title = element_text(size = 16, face = "bold"))
```

p4 <- ggplot() +

  scale_x_continuous(name = "Year+1", expand = c(0,0.1), limits = c(1981,1995), breaks = c(seq(1981, 1995, 3))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.21,0.75)) +
  scale_color_manual(name = "Species Model", 
                     values = c(ac = "#BC8DA0", gh = "#048BA8"),
                     labels = c(ac = "Cod/ Plaice", gh = "Greenland halibut")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  ggtitle("e) Fall") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.position = "none",
        legend.text = element_text(size = 11), legend.title = element_text(size = 16, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
        plot.title = element_text(size = 16, face = "bold"))
```

@@

  geom_line(aes(x = 0, y = 0, colour = "ac"), size = 1.5) +
  geom_point(aes(x = 0, y = 0, colour = "ac"), size = 1.5) +

@@

  scale_x_continuous(name = "Year", expand = c(0,0.1), limits = c(1995,2021), breaks = c(seq(1995, 2021, 5))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.6,2.4)) +
  scale_color_manual(name = "Species Model",
                     breaks = c("all", "surv", "ac", "gh", "ap"), 
                     values = c(all = "black", surv = "#BB2D05", ac = "#BC8DA0", gh = "#048BA8", ap = "#FF7733"),
                     labels = c(all = "All species", surv = "Acoustic survey", ac = "Cod/ Plaice", gh = "Greenland halibut", ap = "American plaice")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  ggtitle("d) Spring") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        # legend.position = "none",
        legend.text = element_text(size = 13), legend.title = element_text(size = 15, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
        plot.title = element_text(size = 16, face = "bold"))
```

@@

p6 <- ggplot() +
  geom_ribbon(data = ts_df, aes(x = acc_year, y = ts, ymin = low_sd, ymax = high_sd), alpha = 0.2) +
  geom_point(data = ts_df, aes(x = acc_year, y = ts, colour = "all")) +
  geom_line(data = ts_df, aes(x = acc_year, y = ts, colour = "all" ), size = 1.5) +

  scale_x_continuous(name = "Year+1", expand = c(0,0.1), limits = c(1995,2022), breaks = c(seq(1995, 2022, 5))) + 
  scale_y_continuous(name = "NLFPM Abundance Index", expand = c(0,0), limits = c(0.45, 1.08)) +
  scale_color_manual(name = "Species Model", values = c(all = "black"),
                     labels = c(all = "All species")) +
  guides(colour = guide_legend(keyheight = 0.4, default.unit = "cm")) +
  ggtitle("f) Fall") +
  theme_classic() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.position = "none",
        legend.text = element_text(size = 9), legend.title = element_text(size = 11, face = "bold"), legend.spacing.x = unit(0,'cm'),
        axis.text = element_text(size = 11), axis.title = element_text(size = 13,face = "bold"),
        plot.title = element_text(size = 16, face = "bold"))
```

@@

p7 <- ggarrange(p1+theme(axis.title.x = element_blank()),
                p2+theme(axis.title.x = element_blank(), axis.title.y = element_blank()),
                p3,
                p5+theme(axis.title.y = element_blank()),
                p4,
                p6+theme(axis.title.y = element_blank()),
                nrow = 3, ncol = 2,
                align = "v", common.legend = TRUE,
                legend = "right", legend.grob = ggpubr::get_legend(p5+theme(legend.position = "right")))

@@

# Linear relationship 
fit <- lm(acc_bm~NLFPM_bm, data = lr_dat)
cor.test(x = lr_dat$NLFPM_bm, y = lr_dat$acc_bm, method = "pearson") # p-values < 0.05: acoustic and NLFPM are significantly correlated 
lr_dat <- na.omit(lr_dat)

@@

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1995,2020), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
  ggtitle("Campelen\na) Fall 2J3KL All Speices") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = "none",
    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

@@

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1995,2020), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
  ggtitle(" \nb) Spring 3L Plaice") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

@@

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1995,2020), midpoint = 2007,  low = "blue", mid = "#FFAEFF", high = "red") +
  theme_classic() +
  ggtitle(" \nc) Spring 3L Halibut") +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
        legend.position = 'none',
        legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
        axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

@@

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1981,1995), midpoint = 1987,  low = "blue", mid = "#FFAEFF", high = "red") +
  ggtitle("Engel\nd) Fall 2J3KL Cod/Plaice") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

@@

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1981,1995), midpoint = 1987,  low = "blue", mid = "#FFAEFF", high = "red") +
  theme_classic() +
  ggtitle(" \ne) Fall 2J3KL Halibut") +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

@@

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring  Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1984,1995), midpoint = 1990,  low = "blue", mid = "#FFAEFF", high = "red") +
  ggtitle("\nf) Spring 2J3KL Cod/Plaice") +
  theme_classic() +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))

@@

  scale_x_continuous(name = "NLFPM Abundance Index", expand = c(0.01,0)) +
  scale_y_continuous(name = "3L Spring Acoustic Capelin Biomass (kt)") +
  scale_colour_gradient2(name = "Year", limits = c(1984,1995), midpoint = 1990,  low = "blue", mid = "#FFAEFF", high = "red") +
  theme_classic() +
  ggtitle(" \ng) Spring 2J3KL Halibut") +
  theme(
    panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),   
    legend.position = 'none',
    legend.text = element_text(size = 11), legend.title = element_text(size = 13, face = "bold"),
    axis.text =  element_text(size = 11), axis.title = element_text(size = 13, face = "bold"),
    plot.title = element_text(size = 13, face = "bold"))
```

@@

p17 <- ggarrange(p15,p16,
          nrow = 2, ncol = 1, align = "v")

@@
